Curriculum and Transfer Learning of Hierarchical Locomotion Policies

### 2018-05-24 paper/main.tex
Add more related work
Add more references / paper summaries

@@

\begin{itemize}
  \item The aforementioned paper \cite{heess2017emergence} trains their policies using curriculum learning: the environment gets progressively more difficult as time goes on.
    This achieves great results, but they do not quite succeed on bumpy ground.
    In this project, we hope to explore hierarchical policies as a potential solution to this difficult task.

@@

\begin{itemize}
  \item We might want to use something simple, like a linear controller as proposed by Ben Recht \cite{mania2018simple} to see if that works well.
    It seems to do a good job on OpenAI benchmarks, at least.
  \item Otherwise, we'll probably end up using TRPO or PPO or something (get citation later\dots)
  \item Other things to consider: prioritized experience replay, hindsight experience replay, universal value function approximators.
\end{itemize}

>>>>

  \item \cite{peng2017learning} uses bumpy ground to test robustness of learned policies, but again the bumps are not actually perceived and cannot be planned around. The bump height thus must remain small relative to the agent. \highlight{We should compare this quantitatively, later.} Also, this is 2D.
\end{itemize}

@@

\begin{itemize}
  \item \cite{karpathy2012curriculum} \highlight{TODO: read this}

  \item The aforementioned paper \cite{heess2017emergence} trains their policies using curriculum learning: the environment gets progressively more difficult as time goes on.
    This achieves great results, but they do not quite succeed on bumpy ground.
    In this project, we hope to explore hierarchical policies as a potential solution to this difficult task.

@@

\begin{itemize}
  \item At the lowest level, we will probably be using some kind of stable PD controller, in order to make the reinforcement learning problem as easy as possible. I need to read these papers: \cite{tan2011stable}, \cite{shrivastava2013stable}
  \item \cite{peng2015terrain} introduces a very interesting way of parametrizing the action space in terms of reference points for PD controllers, as well as ``virtual forces''. We will want to do something similar.
  \item We might want to use something simple, like a linear controller as proposed by Ben Recht \cite{mania2018simple} to see if that works well.
    It seems to do a good job on OpenAI benchmarks, at least.
  \item Otherwise, we'll probably end up using TRPO or PPO or something (get citation later\dots)
  \item Other things to consider: prioritized experience replay, hindsight experience replay, universal value function approximators.
\end{itemize}

\subsection*{Miscellaneous}

Other things I should read / potential baselines to compare against.
\cite{de2010feature} \cite{mordatch2010robust} \cite{mordatch2012discovery}
